---
title: "Project proposal"
author: "Disco"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dsbox)
library(ggridges)
library(ggplot2)
library(readr)
library(here)
library(scales)
library(dplyr)
```


```{r data}
video_game_sales <- read_csv(here::here("data/Video_Games_Sales_as_at_22_Dec_2016.csv"))
```

## 1. Introduction

Our question is:
what factor influences the sales of a video game the most. 

Data is collected from https://www.kaggle.com/rush4ratio/video-game-sales-with-ratings 

(This dataset contains a list of video games with sales greater than 100,000 copies.)

## 2. Data
```{r data-glimpse}
video_game_sales <- read_csv(here::here("data/Video_Games_Sales_as_at_22_Dec_2016.csv"))
glimpse(video_game_sales)
```

## 3. Data analysis plan 

We will look at the different relationships between the sales (global and specific) of a game and different factors in its release and success. All sorts of different plots (e.g. line plot, density plot, bar plot etc.) and data analysis methods (mean, median and mode) will be used to discuss this and visualize this in our different individual ways.

IN GENERAL, WE ARE ANSWERING THE QUESTION:

"WHAT FACTOR HAS THE BIGGEST INFLUENCE OF SALES ON VIDEO GAMES?"

It will follow the ensuing format:


```{r top-of-category}
top_genre <- video_game_sales%>%
  group_by(Genre)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 5)
  
top_genre_list <<- top_genre$Genre

top_platform <- video_game_sales%>%
  group_by(Platform)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 10)
  
top_platform_list <<- top_platform$Platform

top_games <- video_game_sales%>%
  group_by(Name)%>%
  summarise(sales = sum(Global_Sales))%>%
  slice_max(sales, n = 50)

top_games_list <<- top_games$Name

```

### First Data

#### A line graph showing the relationship between genre of game and TOTAL global sales over the years

This plot will clearly show the best genre (in terms of global sales) over the years. From this we can determine how much genre influences the sales over time and classify any trends for particular time periods.

#### code and plotting: a single line graph with top 5 genres and faceted graphs

```{r }
genre_sales_yrs <- video_game_sales%>%
  group_by(Year_of_Release, Genre)%>%
  filter(!Year_of_Release == "N/A") %>%
  filter(!is.na(Genre)) %>%
  summarise(Year_of_Release, Genre, Global_Sales = sum(Global_Sales))%>%
  group_by(Genre)%>%
  filter(Genre %in% top_genre_list) %>%
  distinct()

genre_sales_yrs$Year_of_Release <- as.numeric(as.character(genre_sales_yrs$Year_of_Release))

genre_sales_yrs%>%
  ggplot(aes(x = Year_of_Release, y = Global_Sales, color = Genre, group = Genre)) +
  theme(axis.text.x = element_text(angle = 45, size = 6)) +
  geom_line()+
  scale_x_continuous(name ="Year of release", breaks=seq(1980, 2020, 5))+
  scale_y_continuous(name ="Total global sales", breaks=seq(0, 150, 50))
```
This plot clearly shows that, from the top 5 best selling genres of the data, sports and action games have the biggest peaks (approximately 135 million global sales). But we can also see that these genres have not always been the best selling: while they have not had the best selling in the past 15 years, platform games have consistently achieved a large amount of global sales (for the entirety of the period between 1984 and 1995, it was by far the best selling genre). Yet in the most recent years, games of the platforming genre have certainly been dropping off in sales.

### Second Data

#### A facet graph of mean sale for different area against (top 10) platform(x = platform, y = mean sale) by bar plot or histogram plot

This plot will show us, not only the most successful platform (the platform with the highest mean global sales) but also where these sales come from: the splitting of the mean sales to region will show where particular platforms perform especially well and where they do not. This will allow us to determine how much platforms in certain regions will influence the global sales of a game.

#### code and plotting.

```{r Mean_sale_vs_platform, echo=FALSE}
mean_df <- video_game_sales %>%
  group_by(Platform) %>%
  summarise(mean_NA = mean(NA_Sales), mean_EU = mean(EU_Sales), mean_JP = mean(JP_Sales), mean_Other = mean(Other_Sales), mean_sales = mean(Global_Sales))%>%
  group_by(Platform)%>%
  filter(Platform %in% top_platform_list)
```

```{r pivot_longer_mean_df, echo=FALSE}
mean_df_long <- mean_df%>%
  pivot_longer(
    cols = -Platform,
    names_to = "Region",
    values_to = "meanValue"
  )
```

```{r mean_df_plot}
mean_df_long %>%
  #ggplot(aes(x=Platform))+
  # geom_point(aes(y=mean_sales, colour = "Global"))+
  # geom_point(aes(y=mean_NA, colour = "North America"))+
  # geom_point(aes(y=mean_JP, colour = "Japan"))+
  # geom_point(aes(y=mean_EU, colour = "Europe"))+
  # geom_point(aes(y=mean_Other, colour = "Other"))
  ggplot(aes(x = Platform, y = meanValue, fill = Region, group = Region)) +
  geom_bar(stat="identity", position='dodge')+
  theme(axis.text.x = element_text(angle = 45, size = 6))
```
### Analysis

From the plot, we can see that, overall, north america contributes the most to the global sales of video games across most platforms; excluding the PS4 and PC (for which the highest mean sales is Europe), North America is the biggest seller of video games across platforms. This will be due to a mix of large population and a high percentage of said population with access to these consoles. The opposite can be said about the lower end: Japan and 'Other' regions are on the lower end of mean sales for all platforms: they, in this context, have lower populations and lower percentage of said populations with access to these consoles and therefore it makes sense that they do not contribute as highly to the total global sales of video games across all platforms.

### Third Data

#### A bar chart presenting the relationship between the pubisher and the mean global sales, which contains the ten most popular Publishers in world.. (x = Publisher, y = mean_JP_Sales).

#### code and plotting

```{r }
global_sales_publisher_top10 <- video_game_sales %>%
  group_by(Publisher) %>%
  summarise(mean_global_Sales = mean(Global_Sales)) %>%
  arrange(desc(mean_global_Sales)) %>%
  slice(1:10)
  
global_sales_publisher_top10 %>%
  ggplot(aes(x = Publisher, y = mean_global_Sales, fill = Publisher)) + 
  geom_bar(stat = "identity") +
  labs(title = "The ten most popular Publishers in world",
       x = "Publisher", y = "mean global Sales"
       ) +
  theme_minimal() +
  theme(axis.text.x = element_blank())

```
From the bar chart, we can know that the publisher called palcom has the highrest 
### Fourth Data

#### A comparison graph of critic score and global sales (x variable = critic score, y variable = global sales) and how they relate to each other using a line graph.

This plot will show the relationship between critic score and global sales. It will help visualize how critic score affects global sales - if critic score has an effect on global sales either negatively or positively.

#### code and plotting

```{r }
sample_data <- video_game_sales %>%
 sample_n(500)

sample_data %>%
  ggplot(aes(x = Critic_Score, y = Global_Sales, col = "red")) +
  geom_jitter()+
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  labs(title = "How critic score relates to global sales",
       x = "Critic Score", y = "Global Sales"
       ) +
  theme_minimal() + theme(legend.position = "none")

```

### Analysis

From the graph shown above, we can see that critic score affects global sales positively i.e, the higher the critic score, the more the global sales are. This aligns with something we could have already predicted before. Here, I have taken a sample of 500 random observations from 16719 observations. This is because plotting a graph with 16719 observations did not seem to show a very clear trend. So this shows a different graph every time as it picks a random bunch of 500 observations but in almost every single graph, we see a positive trend. We can also see a lot of critic scores which barely affects the global sales. For example we can see critic score of above 60 which correlates to global sale of 0. This shows we can not really depend on critic scores to see how global sales are affected by it. Therefore we can conclude that critic score is most definitetly, not one of the factors which will have the biggest influence on video games.   

### Fifth data

#### A comparison graph of user score and global sales (x variable = critic score, y variable = global sales) and how they relate to each other using a line graph.

This plot will show the relationship between user score and global sales. It will help visualize how user score affects global sales - if critic score has an effect on global sales either negatively or positively or does not have an effect at all.

#### code and plotting

```{r }
sample_data1 <- video_game_sales %>%
 sample_n(300)

sample_data1$User_Score <- as.numeric(as.character(sample_data1$User_Score))

sample_data1 %>%
  ggplot(aes(x = User_Score, y = Global_Sales, color = "red")) +
  geom_jitter()+
  geom_smooth(method = "lm", se = FALSE, col = "darkgreen") +
  labs(title = "How user score relates to global sales",
       x = "User Score", y = "Global Sales"
       ) +
  theme_minimal() + theme(legend.position = "none")

```

### Analysis

From the graph shown above, we can see that user score does not really have an impact on global sales. Here, I have taken a sample of 300 random observations from 16719 observations. This is because plotting a graph with 16719 observations did not seem to show a very clear trend. So this shows a different graph every time as it picks a random bunch of 300 observations. But in almost every single graph generated, we can sometimes see a positive trend, or not see a trend at all i.e the gradient is zero. Therefore we can conclude that user score is definitely not one of the factors which will have the biggest influence on video games. If we were to compare user score and critic score, user score would be the least influecing factor out of the two.

### Sixth Data

#### A bar plot of Publishers of the high selling games(top 50) across the world.

#### code and plotting

```{r }
high_selling_games <- video_game_sales %>%
  filter(Name %in% top_games_list)%>%
  group_by(Name = tolower(Name)) %>%
  summarise_each(funs(max))%>%
  summarise(Publisher, Global_Sales)
high_selling_games %>%
  group_by(Publisher) %>%
  ggplot(aes(x = Publisher, fill = Publisher)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 10, size = 6),
        legend.position = "none") +
  labs(title = "Publisher of top 50 high saleing games", subtitle = "and the amount of game released")
```
We can see that Nintendo have the most game in top 50 high selling games, its about 20+ and in total there is 9 publishers having game in the top 50. Where other publisher are all having games less than 10. So we can see that the game published by Nintendo are having more sales, where Nintendo is such a large company which having a large amount of money so the game published from Nintendo do have a higher quality.

### Seventh data

#### A list of mean global sales per genre, with box plot to show clearly the spread for each genre

#### code and plotting

```{r }
mean_Genre_video_game <- video_game_sales %>%
  group_by(Genre) %>%
  summarise(global_sales_mean = mean(Global_Sales)) 

mean_Genre_video_game %>%
  ggplot(aes(x = Genre, y= global_sales_mean)) +
  geom_boxplot() +
  labs(title = "mean global sales per genre",
       x = "", y = "Mean Global Sales"
       ) +
  theme(axis.text.x = element_text(angle = 30, size = 10)) +
  theme_minimal() 
  
  
```
we can see that the publishers called Action has the lowest mean global sales among the 11 genres. Most mean global sales of genres are around 0.5. 





### Comparison of all different data and analogies

### Written summary of what factor is mostly tied with global sales with visual proofs (plots)
