---
title: "Project proposal"
author: "Disco"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dsbox)
library(ggridges)
library(here)
library(readr)
```

#RUN THIS IN CONSOLE FOR DATA:
#video_game_sales <- #read_csv("proposal/Video_Games_Sales_as_at_22_Dec_2016.csv")
#View(video_game_sales)

*For instructions on what each section should include, please see the [project page](https://idsed.digital/assessments/project/#proposal) on the course website. Remove this text when completing your proposal*.

## 1. Introduction

Our question is:
what factor influences the sales of a video game the most

## 2. Data
```{r data-glimpse}
glimpse(video_game_sales)
```
## 3. Data analysis plan

We will look at the different relationships between the sales (global and specific) of a game and different factors in its release and success. All sorts of different plots (e.g. line plot, density plot, bar plot etc.) and data analysis methods (mean, median and mode) will be used to discuss this and visualize this in our different individual ways.

