---
title: "Project proposal"
author: "Disco"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dsbox)
library(ggridges)
library(ggplot2)
library(readr)
library(here)
library(scales)
library(dplyr)
```


```{r data}
video_game_sales <- read_csv(here::here("data/Video_Games_Sales_as_at_22_Dec_2016.csv"))
```

## 1. Introduction

Our question is:
what factor influences the sales of a video game the most. 

Data is collected from https://www.kaggle.com/rush4ratio/video-game-sales-with-ratings 

(This dataset contains a list of video games with sales greater than 100,000 copies.)

## 2. Data
```{r data-glimpse}
video_game_sales <- read_csv(here::here("data/Video_Games_Sales_as_at_22_Dec_2016.csv"))
glimpse(video_game_sales)
```

## 3. Data analysis plan 

We will look at the different relationships between the sales (global and specific) of a game and different factors in its release and success. All sorts of different plots (e.g. line plot, density plot, bar plot etc.) and data analysis methods (mean, median and mode) will be used to discuss this and visualize this in our different individual ways.

IN GENERAL, WE ARE ANSWERING THE QUESTION:

"WHAT FACTOR HAS THE BIGGEST INFLUENCE OF SALES ON VIDEO GAMES?"

It will follow the ensuing format:

To be implemented as a function/script 
[top_n(category_1, category2, number) -> {data frame of top `number` variables in the `category_1` category with the `category_2` category values}

```{r top-of-category}
top_genre <- video_game_sales%>%
  group_by(Genre)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 5)
  
top_genre_list <<- top_genre$Genre

top_platform <- video_game_sales%>%
  group_by(Platform)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 10)
  
top_platform_list <<- top_platform$Platform
```

### First Data

#### A line graph showing the relationship between genre of game and TOTAL global sales over the years

This plot will clearly show the best genre (in terms of global sales) over the years. From this we can determine how much genre influences the sales over time and classify any trends for particular time periods.

#### code and plotting: a single line graph with top 5 genres and faceted graphs

```{r }
genre_sales_yrs <- video_game_sales%>%
  group_by(Year_of_Release, Genre)%>%
  filter(!Year_of_Release == "N/A") %>%
  filter(!is.na(Genre)) %>%
  summarise(Year_of_Release, Genre, Global_Sales = sum(Global_Sales))%>%
  group_by(Genre)%>%
  filter(Genre %in% top_genre_list) %>%
  distinct()

genre_sales_yrs%>%
  ggplot(aes(x = Year_of_Release, y = Global_Sales, color = Genre, group = Genre)) +
  theme(axis.text.x = element_text(angle = 45, size = 6)) +
  geom_line()
```
This plot clearly shows that, from the top 5 best selling genres of the data, sports and action games have the biggest peaks (approximately 135 million global sales). But we can also see that these genres have not always been the best selling: while they have not had the best selling in the past 15 years, platform games have consistently achieved a large amount of global sales (for the entirety of the period between 1984 and 1995, it was by far the best selling genre). Yet in the most recent years, games of the platforming genre have certainly been dropping off in sales.

### Second Data

#### A facet graph of mean sale for different area against (top 10) platform(x = platform, y = mean sale) by bar plot or histogram plot

This plot will show us, not only the most successful platform (the platform with the highest mean global sales) but also where these sales come from: the splitting of the mean sales to region will show where particular platforms perform especially well and where they do not. This will allow us to determine how much platforms in certain regions will influence the global sales of a game.

#### Possibly change to bars for clarity

#### code and plotting.

```{r Mean_sale_vs_platform}
mean_df <- video_game_sales %>%
  group_by(Platform) %>%
  summarise(mean_NA = mean(NA_Sales), mean_EU = mean(EU_Sales), mean_JP = mean(JP_Sales), mean_Other = mean(Other_Sales), mean_sales = mean(Global_Sales))%>%
  group_by(Platform)%>%
  filter(Platform %in% top_platform_list)
```

```{r pivot_longer_mean_df}
mean_df_long <- mean_df%>%
  pivot_longer(
    cols = -Platform,
    names_to = "Region",
    values_to = "mean value"
  )
```

```{r mean_df_plot}
mean_df %>%
  ggplot(aes(x=Platform))+
  theme(axis.text.x = element_text(angle = 45, size = 6)) +
  geom_point(aes(y=mean_sales, colour = "Global"))+
  geom_point(aes(y=mean_NA, colour = "North America"))+
  geom_point(aes(y=mean_JP, colour = "Japan"))+
  geom_point(aes(y=mean_EU, colour = "Europe"))+
  geom_point(aes(y=mean_Other, colour = "Other"))
  #+ ggplot(aes(x=Platform, y=mean_sales, group = 1))+
  # geom_bar(stat="identity")
```
From the plot, we can see that, overall, north america contributes the most to the global sales of video games across most platforms; excluding the PS4 and PC (for which the highest mean sales is Europe), North America is the biggest seller of video games across platforms. This will be due to a mix of large population and a high percentage of said population with access to these consoles. The opposite can be said about the lower end: Japan and 'Other' regions are on the lower end of mean sales for all platforms: they, in this context, have lower populations and lower percentage of said populations with access to these consoles and therefore it makes sense that they do not contribute as highly to the total global sales of video games across all platforms.

### Third Data

#### A point gragh presenting the relationship between the pubisher and the mean japan's sales, which are the  top five ones. (x = Publisher, y = mean_JP_Sales).

#### code and plotting

```{r }
video_game_sales %>%
  group_by(Publisher) %>%
  summarise(mean_JP_Sales = mean(JP_Sales)) %>%
  arrange(desc(mean_JP_Sales)) %>%
  slice(1:5) %>%
  ggplot(aes(x = Publisher, y = mean_JP_Sales)) +
  geom_point() +
  labs(title = "The five most popular Publishers in Japan",
       x = "Publisher", y = "mean_JP_Sales"
       ) +
  theme_minimal() 

```

### Fourth Data

#### A comparison graph of critic score and global sales (x variable = critic score, y variable = global sales) and how they relate to each other using a line graph.

#### code and plotting

```{r }
sample_data <- video_game_sales %>%
 sample_n(500)

sample_data %>%
  ggplot(aes(x = Critic_Score, y = Global_Sales)) +
  geom_jitter()+
  labs(title = "How critic score relates to global sales",
       x = "Critic Score", y = "Global Sales"
       ) +
  theme_minimal() 

```

### Fifth Data

#### A scatter graph comparing the user count and user score alongside the same of comparing the critic count and critic score. Colour coded by global sales amount

#### code and plotting

```{r }


```

### Sixth Data

#### A bargraph of Publishers of the high selling games(top 50) across the world.

#### code and plotting

```{r }
high_selling_games <- video_game_sales %>%
  filter(11.3 < Global_Sales)
high_selling_games %>%
  group_by(Publisher) %>%
  ggplot(aes(x = Publisher)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 10, size = 6)) +
  labs(title = "Publisher of top 50 high saleing games", subtitle = "and the amount of game released")
```
We can see that Nintendo have the most game in top 50 high selling games, its about 30+ and in total there is 5 publisher having game in the top 50. Where other publisher are all having games less than 10.

### Seventh data

#### A list of mean global sales per genre, with box plot to show clearly the spread for each genre

#### code and plotting

```{r }


```


### Eigth data

#### A comparison of global sales for games that were released in america against those that were not (simple 2 varaible bar graph with stacked year of release)

#### code and plotting

```{r }


```


### etc...


### Comparison of all different data and analogies

### Written summary of what factor is mostly tied with global sales with visual proofs (plots)
