---
title: "The factors affecting sales of video games"
subtitle: <font size='6'>From 1980 to 2020</font>
author: <font size='8'>Disco <br> Adam, Aishee, Haoran, Karl</font>
institute: <font size='10'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)

library(broom)
library(dsbox)
library(ggridges)
library(ggplot2)
library(readr)
library(here)
library(scales)
library(dplyr)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
video_game_sales <- read_csv(here::here("data/Video_Games_Sales_as_at_22_Dec_2016.csv"))
```

```{r top-of-category, include=FALSE}
top_genre <- video_game_sales%>%
  group_by(Genre)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 5)
  
top_genre_list <<- top_genre$Genre

top_platform <- video_game_sales%>%
  group_by(Platform)%>%
  summarise(global = sum(Global_Sales))%>%
  slice_max(global, n = 10)
  
top_platform_list <<- top_platform$Platform

top_games <- video_game_sales%>%
  group_by(Name)%>%
  summarise(sales = sum(Global_Sales))%>%
  slice_max(sales, n = 50)

top_games_list <<- top_games$Name

```

# A statement of our overall goal: {data-background-image="img/gamecontr.png"}

- We will look at the different relationships between the sales (global and region specific) of a game and different factors in its release and success.

- The different factors we look at include genre, platform of release, user and critic score.

- We will look at the correlation between each of these factors and decide on the most influential characteristic in the sales of a game.

# The correlation between genre and sales:

::: columns
:::: {.column width="35%"}
* We have produced a line graph showing the relationship between genre of game and total global sales over the years
* goes here
::::

:::: {.column width="65%"}
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
genre_sales_yrs <- video_game_sales%>%
  group_by(Year_of_Release, Genre)%>%
  filter(!Year_of_Release == "N/A") %>%
  filter(!is.na(Genre)) %>%
  summarise(Year_of_Release, Genre, Global_Sales = sum(Global_Sales))%>%
  group_by(Genre)%>%
  filter(Genre %in% top_genre_list) %>%
  distinct()

genre_sales_yrs%>%
  ggplot(aes(x = Year_of_Release, y = Global_Sales, color = Genre, group = Genre)) +
  theme(axis.text.x = element_text(angle = 45, size = 6)) +
  geom_line()
```
::::
:::

# Data 6 - Adam


# Data 3 - Karl


# Data 7 - Karl


# Data 4 - Aishee


# Data 5 - Aishee


# Data 2 - Haoran

```{r Mean-sale-vs-platform, echo = FALSE}
mean_df <- video_game_sales %>%
  group_by(Platform) %>%
  summarise(mean_NA = mean(NA_Sales), mean_EU = mean(EU_Sales), mean_JP = mean(JP_Sales), mean_Other = mean(Other_Sales), mean_sales = mean(Global_Sales)) %>%
  group_by(Platform) %>%
  filter(Platform %in% top_platform_list)
```

```{r pivot-longer-mean-df, echo=FALSE}
mean_df_long <- mean_df %>%
  pivot_longer(
    cols = -Platform,
    names_to = "Region",
    values_to = "meanValue"
  )
```

```{r mean-df-plot, echo = FALSE}
mean_df_long %>%
  ggplot(aes(x = Platform, y = meanValue, fill = Region, group = Region)) +
  geom_bar(stat="identity", position='dodge')+
  theme(axis.text.x = element_text(angle = 45, size = 6))
```

## Explaination
::: columns
:::: column
* Some text
* goes here
::::

:::: column
```{r Mean-sale-vs-platform-data, echo = FALSE}
mean_df <- video_game_sales %>%
  group_by(Platform) %>%
  summarise(mean_NA = mean(NA_Sales), mean_EU = mean(EU_Sales), mean_JP = mean(JP_Sales), mean_Other = mean(Other_Sales), mean_sales = mean(Global_Sales)) %>%
  group_by(Platform) %>%
  filter(Platform %in% top_platform_list)
```

```{r pivot-longer-mean-df-data, echo=FALSE}
mean_df_long <- mean_df %>%
  pivot_longer(
    cols = -Platform,
    names_to = "Region",
    values_to = "meanValue"
  )
```

```{r mean-df-plot-data, echo = FALSE}
mean_df_long %>%
  ggplot(aes(x = Platform, y = meanValue, fill = Region, group = Region)) +
  geom_bar(stat="identity", position='dodge')+
  theme(axis.text.x = element_text(angle = 45, size = 6))
```
::::
:::

# Conclusion - Haoran


# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

# Using reveal.js

It's possible to have a horizontal sliding transition as well as nest multiple slides to create a vertical stack.

When presenting, you use the left/right arrows to step through the top-level (horizontal) slides. When you arrive at a vertical stack you can optionally press the up/down arrows to view the vertical slides or skip past them by pressing the right arrow.

(click the down key now)

## reveal.js

- The presentation is created using the `reveal.js` package

- You can create a slide show broken up into sections by using the # and ## heading tags

- You can also create a new slide without a header using a horizontal rule (----)

----

- You can also add pauses between content on a slide using (". . .")

. . .

Like this.

...or using "::: fragment"

::: fragment

Like this.

:::

# Layouts

You can use plain text

- or bullet points

<div>
  <div style="float: left; width: 50%;">or text in two columns</div>
  <div style="float: left; width: 50%;">like this</div>
</div>

because you can combine HTML and Markdown syntax.

<p style="font-size: 8pt; position: absolute; bottom: -5em; width: 100%; text-align: center;">*You can also add footnotes</p>

# Code

```{r boring-regression}
# a boring regression
model <- lm(dist ~ speed, data = cars)
tidy(model)
glance(model)
```

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

## Plot and text

::: columns
:::: column
* Some text
* goes here
::::

:::: column
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

## Different widths

::: columns
:::: {.column width="40%"}
* Some text
* goes here
::::

:::: {.column width="60%"}
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

## {data-background-image="https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80"}
